Setup_OMs

### 2023-09-22 Ecov_study/catchability/Setup_OMs.Rmd
Change OM numbering labels.

# Factorial combinations
OMsetup <- expand.grid(Ecov_process_sig = Ecov_process_sig, Ecov_process_cor = Ecov_process_cor, Ecov_process_obs_sig = Ecov_process_obs_sig, Ecov_effect = Ecov_effect, F_hist = F_hist, ageComp_sig = ageComp_sig, log_index_sig = log_index_sig, log_catch_sig = log_catch_sig)
OMsetup
```

@@

  # Finish setup & save OM
  OM <- NULL # Clear prior OM object just in case
  OM <- fit_wham(input = inputOM, do.fit = FALSE, MakeADFun.silent = TRUE)
  mkdir(here::here("Results", paste0("OM_", iom))) # set up storage
  saveRDS(OM, file = here::here("Results", paste0("OM_", iom), paste0("OM_", iom, ".Rds"))) # save OM
  saveRDS(OMsetup[iom,], file = here::here("Results", paste0("OM_", iom), "OMsettings.Rds")) # save OM settings in a separate file since naming is based on arbitraty order in OMsetup table

>>>>

# Factorial combinations
OMsetup <- expand.grid(Ecov_process_sig = Ecov_process_sig, Ecov_process_cor = Ecov_process_cor, Ecov_process_obs_sig = Ecov_process_obs_sig, Ecov_effect = Ecov_effect, F_hist = F_hist, ageComp_sig = ageComp_sig, log_index_sig = log_index_sig, log_catch_sig = log_catch_sig)

OMname <- 1:nrow(OMsetup)

OMsetup <- cbind(OMname, OMsetup)

OMsetup
```

@@

  # Finish setup & save OM
  OM <- NULL # Clear prior OM object just in case
  OM <- fit_wham(input = inputOM, do.fit = FALSE, MakeADFun.silent = TRUE)
  mkdir(here::here("Results", paste0("OM_", OMsetup$OMname[iom]))) # set up storage
  saveRDS(OM, file = here::here("Results", paste0("OM_", OMsetup$OMname[iom]), paste0("OM_", OMsetup$OMname[iom], ".Rds"))) # save OM
  saveRDS(OMsetup[iom,], file = here::here("Results", paste0("OM_", OMsetup$OMname[iom]), "OMsettings.Rds")) # save OM settings in a separate file since naming is based on arbitraty order in OMsetup table
